---
title: "H3: Cultural Differences in Symbolization"
author: "Mariola Paruzel-Czachura, Cillian McHugh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }


</style>


```{r setuph3, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
```


```{r}
rm(list = ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(papaja)
library(purrr)
#install.packages("interactions")
library(interactions)
library(kableExtra)
#devtools::install_github("crsh/papaja")
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
#install.packages("reshape")
library(reshape)
library(corx)
library(lsr)
#install.packages("Cairo")
#library(Cairo)
library(foreign)
library(ltm)
library("ggpubr")
#install.packages("rworldmap")
library(rworldmap)
#devtools::install_github("rensa/ggflags")
library(ggflags)
#devtools::install_github("schliebs/ggoxford")
library(ggoxford)
library(ggforce)
library(ggbeeswarm)
library(countrycode)
```



```{r}
rm(list = ls())

#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

df$sex3 <- as.factor(df$sex1)
df$sex3 <- dplyr::recode(df$sex3,
               "1"="male"
              ,"2"="female"
              ,"3"="other")

df$country_lower <- tolower(df$country)
df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")


x <- df
```


```{r}


# h3a yes
# h3b n/a (competing)
# h3c yes
# h3d no (no relationship)
# h3e yes
# h3f yes
# h3g no, no, yes


x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]

fit0 <- lm(moral_identity_symbolic ~ 
             mean(x$moral_identity_symbolic)
                    # sex3
                    # + age
                    #  Power.Distance
                    # + Individualism
                    # + Masculinity
                    # + Uncertainty.Avoidance
                    # + Long.Term.Orientation
                    # + Indulgence
                    # + CTL_C
                    # + CTL_DS
                    # + CTL_DG
                 , data = x
            ) 

summary(fit0)

fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)
anova(fit)
fit_results <- apa_print(fit)

cor.test(x$Power.Distance,x$moral_identity_symbolic)

fit_results$full_result

```

Our third hypothesis predicted relationships between symbolization and specific cultural variables. The variables question are: power distance, individualism, masculinity, uncertainty avoidance, long term orientation, and indulgence, taken from Hofstede (2001), as well as three measures of cultural tightness (domain-specific, domain-general, and a combination index). These variables were inputted at the country level, and as such, we conducted a hierarchical linear regression model to investigate relationship with symbolization. Symbolization was our outcome measure and each cultural variable was included as a predictor in the model. 
